Mortality Trend Among Shelter Residents: 

### 2024-09-27 paper/paper.qmd
Change the format of the paper for readability

---
title: "Mortality Trend Among Shelter Residents: Closely Tied To Virus Outbreaks"
author: 
  - Mandy He
thanks: "Code and data are available at: https://open.toronto.ca/dataset/deaths-of-shelter-residents/"
date: Septmeber 27 2024
date-format: long
abstract: "Homelessness remain pressing issues in today’s society, particularly evident in downtown Toronto, these individuals often face severe health issues, leading to an increased risk of mortality. This paper analyzes trends in mortality rates among shelter residents in the City of Toronto from 2007 to 2024, highlighting patterns over time and exploring the factors contributing to these rates. This paper found trend in mortality rate of this minority group reflects the overall health conditions in the macro-environment. Therefore, examining these patterns can help improve provisions and reduce the number of deaths among both this vulnerable population and society at large."
format: pdf
number-sections: true
bibliography: references.bib 
toc: true

@@

One notable point is that in the article (@cameron2019), the fatality rate for the 2014-2015 outbreak was only 2.4%, despite the hundreds of flu outbreaks that occurred that year. However,@fig-TotalNumberofDeathByYear shows that the number of deaths in 2015 was around 45. This discrepancy can be explained by the fact that the data in the article pertains to hospital outbreaks, where individuals have access to better medical care. In contrast, homeless individuals may lack the resources to seek treatment, leading to a higher number of deaths in this population.

>>>>

---
title: "Mortality Trend Among Shelter Residents: "
subtitle: "Closely Tied To Virus Outbreaks"
author: 
  - Mandy He
thanks: "Code and data are available at: https://open.toronto.ca/dataset/deaths-of-shelter-residents/"
date: Septmeber 27 2024
date-format: long
abstract: "Homelessness remain pressing issues in today’s society, particularly evident in Toronto, these individuals face severe health issues, leading to increased risk of mortality. This paper analyzes trends in mortality rates among shelter residents in the City of Toronto (2007 to 2024), highlighting patterns over time and exploring the factors contributing to these rates. This paper found trend in mortality rate of this minority group reflects the overall macro-environment health conditions. Thus, examining these patterns can help improve provisions and reduce the number of deaths among both this vulnerable population and society at large."
format: pdf
number-sections: true
bibliography: references.bib 
toc: true

@@

One notable point is that in the article (@cameron2019), the fatality rate for the 2014-2015 outbreak was only 2.4%, despite the hundreds of flu outbreaks that occurred that year. However, @fig-TotalNumberofDeathByYear shows that the number of deaths in 2015 was around 45. This discrepancy can be explained by the fact that the data in the article pertains to hospital outbreaks, where individuals have access to better medical care. In contrast, homeless individuals may lack the resources to seek treatment, leading to a higher number of deaths in this population.
